---
title: "Video validation: process data"
author: "Grace Smith-Vidaurre"
date: "2024-12-01"
output: html_document
---

Purpose: Perform automated integration and scoring of movement data with ABISSMAL over varying data processing and integration parameters. These datasets will be used in subsequent validation analyses in comparison to a manually scored dataset of coarse-grained behaviors as a baseline.

There are a lot of different parameters that can be modified here throughout the pipeline, and things can get messy. It might make the most sense to iterate over the pre-processing and integration parameters to compare the overall activity detected between methods (and coarse-grain the manual scoring data even more to collapse behavioral scores across different subjects for a better 1:1 comparison). Then, use the pre-processing and integration parameters with the closest overall activity levels to the manually scored dataset for the more detailed validation analyses in the next script.
```{r}

knitr::opts_knit$set(eval = TRUE, echo = TRUE)

```

```{r package and paths, warning = FALSE, message = FALSE}

# Clean the global environment
rm(list = ls())

X <- c("tidyverse", "pbapply", "data.table", "tidyquant")

# Install the packages in X if not already installed
is_installed <- function(p) is.element(p, installed.packages()[,1])

invisible(lapply(1:length(X), function(x){
  if(!is_installed(X[x])){
    install.packages(X[x], repos = "http://lib.stat.cmu.edu/R/CRAN")
  }
}))

invisible(lapply(X, library, character.only = TRUE))

# Load the custom functions for computational analyses with ABISSMAL
code_path <- "~/Desktop/GitHub_repos/ABISSMAL/R"
code <- list.files(code_path, pattern = ".R$", full.names = TRUE)

invisible(lapply(1:length(code), function(i){
  source(code[i])
}))

# Overall path: contains the aggregated BORIS spreadsheet in wide format across all video recording events
path <- "~/Desktop/ABISSMAL_validation_data"

# Path to the combined raw movement sensor data
sensor_path <- file.path(path, "raw_combined")

# Initialize a folder where we will save the indexed raw data for the validation analyses
indexed_dir <- "indexed_labeled_data"
indexed_path <- file.path(path, indexed_dir)

# Create this folder if it doesn't already exist
if(!dir.exists(indexed_path)){
  dir.create(indexed_path)
}

seed <- 888

```


TKTK additional pre-processing steps:

1a. Data pre-processing of the switched recording events that Summer identified. Look at the spreadsheet called "BORIS_VideoList_TimeFlipped.csv". We could i) exclude these videos from analyses, or ii) we could try to flip the manual scores given the timestamps of the scores and the videos themselves, or iii) if one video has extremely short duration, then drop the scores for that video in the pair. TKTK keep thinking about a solution

1b. Figure out if we can discriminate videos for which video recording was initialized by daily animal checks (a hand opening the nest container), check the notes column of the aggregated .csv. This will be scored as no birds inside of the containr but may have a very high pixel number that changed. Summer kept track in her log, but this only happened 2-3 times, check the notes of the BORIS .csv, recording event 2322 

Read in the aggregated manual scoring spreadsheet in which each row is a unique behavioral state per subject within a recording event.
```{r}

manual_scoring <- read.csv(file.path(path, "BORIS_ManualScoring_Aggregated_pre-processed.csv"))
glimpse(manual_scoring)

```

Read in the spreadsheet for unmasking the video file names.
```{r}

unmask_nms <- read.csv(file.path(path, "unmasked_video_names.csv"))
glimpse(unmask_nms)

```

Choose a subsample of these videos to develop the validation analysis pipeline.
```{r}

# Randomly select 50 video recording events from the current version of the aggregated manual scoring results in wide format

# First get all of the unique BORIS Observation IDs that correspond to unique recording events
unique_obs_ids <- unique(manual_scoring$Observation.id)
head(unique_obs_ids)

# There should be 4045 Observation IDs to match the unique recording events that Summer scored, looks good
length(unique_obs_ids)

set.seed(seed)
subsample <- sample(unique_obs_ids, 50, replace = FALSE)

subsample

```

Next, unmask the video file names used for manual scoring.
```{r}

manual_scoring_ss <- manual_scoring %>% 
  dplyr::filter(Observation.id %in% subsample)

dim(manual_scoring_ss)

# Checking filtering, looks good
# all(unique(manual_scoring_ss$Observation.id) %in% subsample)
# all(subsample %in% unique(manual_scoring_ss$Observation.id))

# Add the unmasked video file names to each observation in the manual scoring spreadsheet
# i <- 1 # testing
manual_scoring_nm <- data.table::rbindlist(pblapply(1:nrow(manual_scoring_ss), function(i){
  
  # Get the masked video recording event ID
  masked_nm <- manual_scoring_ss$masked_video_recording_event_ID[i]
  # masked_nm
  
  # Use the masked video recording event ID to find the unmasked recording event ID per row
  unmasked_nm <- unmask_nms %>% 
    dplyr::filter(masked_name == masked_nm) %>% 
    pull(videos)
  
  # Add the unmasked name back to the manual scoring data frame
  # The unmasked name will be one of the two unique video files per unique recording event (we don't need both names for later steps)
  return(
    manual_scoring_ss[i, ] %>% 
      dplyr::mutate(
        unmasked_video_file = unmasked_nm
      )
  )
  
}))

# Select a few rows at random and manually check the unmasking results
glimpse(manual_scoring_nm)
dim(manual_scoring_nm)
# View(manual_scoring_nm)

```

# Step 1. Coarse-grain the manually scored dataset across individual subjects

In order to compare overall patterns of activity (regardless of the specific behavioral type that was scored) between manual scoring and ABSSMAL automated inference, we need to make sure that the datasets also display a similar level of resolution of individual identity. The manually scored dataset has the finest resolution of individual identity within the video recording events, and even includes individual identity of birds that were not PIT-tagged for individual identity detection via the RFID system. The automated inferences by ABISSMAL, on the other hand, rely on the RFID system only for individual identity detection, and therefore individual identity cannot be resolved for all individuals without PIT-tags (all chicks throughout development). In addition, RFID systems can fail to detect PIT tags (which will be validated in the next script), so the resolution of individual identity of even the two PIT-tagged adults is likely not as high as the manually scored dataset.

For these analyses, we should collapse behavioral scores in the manual dataset across individuals in cases when the automated pipeline would not be able to assign the same behavioral score to separate individuals. The behavioral events for which we expect this to happen are when more than one individual is assigned the behavioral state "INSC" or "inside container". ABISSMAL currently uses the presence of a video recording plus the absence of detections by other movement sensors to infer whether one or more birds was inside of the nest container. Currently, the ABISSMAL functions cannot discriminate whether one bird or more than one bird was inside of the container, nor the individual identity of the bird(s) inside of the container.

All other behaviors scored manually and by ABISSMAL are behaviors that can only be performed by one individual at a time (sequentially), rather than more than one individual concurrently. Perching, entering, and exiting the nest container can only be performed by one individual at a time, given that only one individual fits in the nest container entrance.

Proceed by collapsing the INSC scores in the manual dataset to a single event across individuals. Collapse these scores across individuals even if the timestamps of the INSC events for not fully overlap, since this is a very coarse-grained analysis.

```{r}

glimpse(manual_scoring_nm)

# First, are there video recording events with more than one INSC score across subjects?
# Yes, looks good
manual_scoring_nm %>% 
  dplyr::filter(Behavior == "INSC") %>% 
  group_by(unmasked_video_file) %>% 
  dplyr::summarise(
    n_subjects = length(Subject),
    n_INSC = n()
  ) %>% 
  print(n = nrow(.))

# Retain a single row for INSC scores per unique video recording event
manual_scoring_nm_coll <- manual_scoring_nm %>%
  dplyr::filter(Behavior == "INSC") %>% 
  distinct(unmasked_video_file, Behavior) %>%
  # Add back the rows for all other behavioral scores
  bind_rows(
    manual_scoring_nm %>%
      dplyr::filter(Behavior != "INSC")
  ) %>% 
  arrange(unmasked_video_file)

glimpse(manual_scoring_nm_coll)

# Should have dropped rows after this operation, looks good
nrow(manual_scoring_nm) - nrow(manual_scoring_nm_coll)

```

# Step 2. Iterate over data processing and integration parameters in the ABISSMAL pipeline for automated behavioral inferences

Next, run the ABISSMAL pipeline for automated behavioral inference with movement data. The data pre-processing and integration steps will be performed over varying parameters (such as the temporal thresholds used to find clusters of detections close together, or to remove detections that are close together).

## Read in combined raw data

```{r}

# Read in the raw combined infrared beam breaker detections
irbb_events <- read.csv(file.path(sensor_path, "combined_raw_data_IRBB.csv")) %>% # Make sure that the timestamps are in the right format
  dplyr::mutate(
    timestamp_ms = as.POSIXct(format(as.POSIXct(timestamp_ms, tz = ""), "%Y-%m-%d %H:%M:%OS6")))

glimpse(irbb_events)

# Read in the raw combined RFID detections
rfid_events <- read.csv(file.path(sensor_path, "combined_raw_data_RFID.csv")) %>% # Make sure that the timestamps are in the right format
  dplyr::mutate(
    timestamp_ms = as.POSIXct(format(as.POSIXct(timestamp_ms, tz = ""), "%Y-%m-%d %H:%M:%OS6")))

glimpse(rfid_events)

# Read in the raw combined video detections
video_events <- read.csv(file.path(sensor_path, "combined_raw_data_Video.csv")) %>% # Make sure that the timestamps are in the right format
  dplyr::mutate(
    timestamp_ms = as.POSIXct(format(as.POSIXct(timestamp_ms, tz = ""), "%Y-%m-%d %H:%M:%OS6")))

glimpse(video_events)

```

The next step will be to perform automated behavioral scoring of the raw movement sensor data using the default temporal thresholds for automated data processing and behavioral inference from ABISSMAL computational analyses.

## Perform automated behavioral inference

Here, iterate over different thresholds and run all subsequent ABISSMAL functions per iteration. Save only the final output of `score_clusters`, then remove other temporary files. The `score_clusters` output will be used to compare levels of overall activity over varying pre-processing and integration parameters to the manually scored baseline. 

Find RFID and beam breaker perching events. Iterate over different temporal thresholds used to label stretches of detections as perching events.
```{r find perching events}

# Use these for detect_perching_events for RFID and IRBB data, then pre-process detections for RFID and IRBB, then  
ths <- c(0.1, 0.2, 1, 2, 4) # temporal thresholds in seconds

invisible(pblapply(1:length(ths), function(thx){
  
  detect_perching_events(file_nm = "combined_raw_data_RFID.csv", threshold = ths[thx], run_length = 2, sensor_id_col_nm = "sensor_id", timestamps_col_nm = "timestamp_ms", PIT_tag_col_nm = "PIT_tag_ID", rfid_label = "RFID", outer_irbb_label = NULL, inner_irbb_label = NULL, general_metadata_cols = c("chamber_id", "sensor_id"), path = path, data_dir = "raw_combined", out_dir = "processed", out_file_prefix = paste("perching_events_th-", ths[thx], sep = ""), tz = "", POSIXct_format = "%Y-%m-%d %H:%M:%OS")
  
}))

invisible(pblapply(1:length(ths), function(thx){
  
  detect_perching_events(file_nm = "combined_raw_data_IRBB.csv", threshold = ths[thx], run_length = 2, sensor_id_col_nm = "sensor_id", timestamps_col_nm = "timestamp_ms", PIT_tag_col_nm = NULL, rfid_label = NULL, outer_irbb_label = "Outer Beam Breaker", inner_irbb_label = "Inner Beam Breaker", general_metadata_cols = c("chamber_id", "sensor_id"), path = path, data_dir = "raw_combined", out_dir = "processed", out_file_prefix = paste("perching_events_th-", ths[thx], sep = ""), tz = "", POSIXct_format = "%Y-%m-%d %H:%M:%OS")
  
}))

```

# Pre-processing raw data

Pre-process the RFID, beam breaker, and video data for the indexed detections per sensor. Iterate over different temporal thresholds used to remove beam breaker and RFID detections that were very close together.

TKTK update code, need to either update the function below to include a prefix, or instead run all functions together per temporal threshold and save these in separate directories by threshold value.
```{r preprocess data}

ths <- c(0.1, 0.2, 1, 2, 4) # temporal thresholds in seconds

invisible(pblapply(1:length(ths), function(thx){
  
  # Used thinning with a threshold of 2 seconds for beam breakers as well
  preprocess_detections(sensor = "IRBB", timestamps_col_nm = "timestamp_ms", group_col_nm = "sensor_id", pixel_col_nm = NULL, mode = "thin", thin_threshold = 2, pixel_threshold = NULL, drop_tag = NULL, path = path, data_dir = "raw_combined", out_dir = "processed", tz = "", POSIXct_format = "%Y-%m-%d %H:%M:%OS")
  
}))

# Performed pre-processing with a threshold of 2 seconds for RFID because I removed the timestamp difference rounding
# The PIT tag IDs specified in `drop_tag` were tags I used for testing the RFID antenna and were not used to mark birds
invisible(pblapply(1:length(ths), function(thx){
  
  preprocess_detections(sensor = "RFID", timestamps_col_nm = "timestamp_ms", group_col_nm = "PIT_tag_ID", pixel_col_nm = NULL, mode = "thin", thin_threshold = 2, pixel_threshold = NULL, drop_tag = c("01-10-3F-84-FC", "01-10-16-B8-7F"), path = path, data_dir = "raw_combined", out_dir = "processed", tz = "", POSIXct_format = "%Y-%m-%d %H:%M:%OS")
  
}))

# Used a pixel threshold of 1000 for video data. Since we used 9000 pixels as the sensitivity threshold for motion detection, this filtering threshold will not drop any data
# This filtering should not drop any videos in the indexed data, and looks good, 100 rows remain
preprocess_detections(sensor = "Video", timestamps_col_nm = "timestamp_ms", group_col_nm = NULL, pixel_col_nm = "total_pixels_motionTrigger", mode = NULL, thin_threshold = NULL, pixel_threshold = 1000, drop_tag = NULL, path = path, data_dir = "raw_combined", out_dir = "processed", tz = "", POSIXct_format = "%Y-%m-%d %H:%M:%OS")

```

# Integrate pre-processed data

Find clusters of detections across all 3 movement sensor that represent movement events per.
```{r find detection clusters for 3 sensor types}

# Using camera_label = "Camera" again here since that's was carried through from the raw data
# The run length needs to be set to 1 in order to correctly detect detection clusters of length 2
detect_clusters(file_nms = c("pre_processed_data_IRBB.csv", "pre_processed_data_RFID.csv", "pre_processed_data_Video.csv"), threshold = 2, run_length = 1, sensor_id_col_nm = "sensor_id", timestamps_col_nm = "timestamp_ms", PIT_tag_col_nm = "PIT_tag_ID", rfid_label = "RFID", camera_label = "Camera", preproc_metadata_col_nms = c("thin_threshold_s", "pixel_threshold", "data_stage", "date_pre_processed"), general_metadata_col_nms = c("chamber_id", "year", "month", "day"), video_metadata_col_nms = c("total_pixels_motionTrigger", "video_file_name"), path = path, data_dir = "processed", out_dir = "processed", out_file_nm = "detection_clusters.csv", tz = "", POSIXct_format = "%Y-%m-%d %H:%M:%OS")

```

Score detection clusters to make inferences about behavioral events associated with these movements.  `score_clusters` should be making inferences by just the first edge encountered, not all edges in a sequence, because the system is currently targeted to capturing overall patterns of activity.
```{r score detection clusters for 3 sensor types}

score_clusters(file_nm = "detection_clusters.csv", rfid_label = "RFID", camera_label = "Camera", outer_irbb_label = "Outer Beam Breaker", inner_irbb_label = "Inner Beam Breaker", video_metadata_col_nms = c("total_pixels_motionTrigger", "video_file_name"), integrate_perching = TRUE, perching_dataset = "RFID-IRBB", perching_prefix = "perching_events_", sensor_id_col_nm = "sensor_id", PIT_tag_col_nm = "PIT_tag_ID", pixel_col_nm = "total_pixels_motionTrigger", video_width = 1280, video_height = 720, integrate_preproc_video = TRUE, video_file_nm = "pre_processed_data_Video.csv", timestamps_col_nm = "timestamp_ms", path = path, data_dir = "processed", out_dir = "processed", out_file_nm = "scored_detectionClusters.csv", tz = "", POSIXct_format = "%Y-%m-%d %H:%M:%OS")

```


