---
title: "Pre-process manual scoring data"
author: Grace Smith-Vidaurre
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

*Purpose*: In this script, we pre-processed the spreadsheet containing aggregated BORIS manual video scoring results from all the video recording events used for validation analyses. This pre-processing included fixing typos and checking which videos needed to be rescored for aggregated export. Previously, we had exported video scoring results in tabular format from BORIS before realizing that aggregated export was the only way to uniquely associate behavioral scores with their respective video recording events. A few video recordings events had to be rescored to facilitate aggregated export of results from BORIS.

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE, eval = TRUE, warning = FALSE, messsage = FALSE)

```

Load packages and set paths.
```{r package and paths}

# Clean the global environment
rm(list = ls())

X <- c("tidyverse", "pbapply", "data.table")

invisible(lapply(X, library, character.only = TRUE))

# Path to the aggregated BORIS spreadsheet in wide format across all video recording events
path <- "~/Desktop/ABISSMAL_validation_data"

seed <- 888

```

Read in the aggregated manual scoring spreadsheet in which each row is a unique behavioral state per subject within a recording event.
```{r}

manual_scoring <- read.csv(file.path(path, "BORIS_ManualScoring_Aggregated.csv"))
glimpse(manual_scoring)

# View(manual_scoring)

```

Which video recording events need to be rescored and exported in aggregated format?
```{r}

# Replace dashes with underscores in the observation
manual_scoring$Observation.id <- gsub("-", "_", manual_scoring$Observation.id)

# Also replace observation IDs with duplicated "Observation"
manual_scoring$Observation.id <- gsub("Observation_Observation", "Observation", manual_scoring$Observation.id)

# Also replace other typos in observation IDs
manual_scoring$Observation.id <- gsub("Observatin", "Observation", manual_scoring$Observation.id)

# Which recording events are missing from this spreadsheet?
# x <- 9849 # testing
numeric_video_ids <- sapply(1:nrow(manual_scoring), function(x){
  
  tmp <- strsplit(manual_scoring$Observation.id[x], split = "_")[[1]][2]
  
  return(as.numeric(tmp))
  
}, USE.NAMES = FALSE)

# No NAs in this vector
which(is.na(unique(numeric_video_ids)))

# Which unique recording events are missing from the current aggregated spreadsheet?
all_video_ids <- seq(1, 4045, 1)

wh <- which(!all_video_ids %in% numeric_video_ids)

# These are the video recording IDs that need to be rescored and exported in aggregated format from BORIS before downstream analysis
all_video_ids[wh]

# Check that this is true
pat <- paste("Observation", all_video_ids[wh], sep = "_")
pat

# Search for this pattern in the data frame to be sure. We found no instances of these BORIS observations in the data frame, confirming that these files need to be scored/exported again
grep(paste(paste("^", pat, "$", sep = ""), collapse = "|"), manual_scoring$Observation.id)

# Export the information for videos that need to be scored/exported again
pat %>% 
  write.table(., file = file.path(path, "videos_for_aggregatedExport.txt"), sep = "\t", col.names = FALSE, row.names = FALSE, append = FALSE)

```

Summer used this list to rescore 17 videos and export them to aggregated format, then we read the whole aggregated .csv back in again before fixing typos.

Fix typos in the Observation column and write out the spreadsheet with these typos fixed.
```{r}

# Replace dashes with underscores in the observation
manual_scoring$Observation.id <- gsub("-", "_", manual_scoring$Observation.id)

# Also replace observation IDs with duplicated "Observation"
manual_scoring$Observation.id <- gsub("Observation_Observation", "Observation", manual_scoring$Observation.id)

# Also replace other typos in observation IDs
manual_scoring$Observation.id <- gsub("Observatin|observation|Observaton|Observsation|Observtion", "Observation", manual_scoring$Observation.id)

# Check that this column has no more typos
# x <- 1
labels <- unique(sapply(1:nrow(manual_scoring), function(x){
  
  strsplit(manual_scoring$Observation.id[x], split = "_")[[1]][1]
  
}))

# Looks good
labels

```

Create a new column in the manual scoring spreadsheet that contains the unique recording event ID.
```{r}

manual_scoring2 <- manual_scoring %>%
  # Separate each video within the Source column into two separate columns
  # Throws a warning for 3 row indices that I checked, and all will have an NA in the video_2 column because only a single video is listed in the Source column
  separate(col = Source, sep = ";", into = c("video_1", "video_2"), remove = FALSE) %>% 
  # glimpse()
  dplyr::mutate(
    masked_video_recording_event_ID = gsub("C:/Users/summe/OneDrive/Desktop/Video Scoring/Videos/", "", video_1),
    masked_video_recording_event_ID = gsub("C:/Users/summe/OneDrive/Desktop/Video Scoring/Aggregated Events/Rescore/", "", masked_video_recording_event_ID),
    # Need to escape each blackslash in the pattern to replace with a backslash
    masked_video_recording_event_ID = gsub("player #1:Videos\\\\", "", masked_video_recording_event_ID),
    masked_video_recording_event_ID = gsub("player #1:", "", masked_video_recording_event_ID)
  )

glimpse(manual_scoring2)
# View(manual_scoring2)

# There should be no NAs in the new ID column, looks good
which(is.na(manual_scoring2$masked_video_recording_event_ID))

# Each video recording name in the new ID column should be found in the Source column for the same row, looks good
all(sapply(1:nrow(manual_scoring2), function(x){
  
  grepl(manual_scoring2$masked_video_recording_event_ID[x], manual_scoring2$Source[x])
  
}))


```

Write out the spreadsheet with updated typos.
```{r}

manual_scoring2 %>% 
  write.csv(file.path(path, "BORIS_ManualScoring_Aggregated_pre-processed.csv"), row.names = FALSE)

```

